Verifying Demonstrations

### 2020-03-13 paper/DB-Schnorr-nbit.tex
Fixes some equations that breaks boxes
Better framing of l-bits problem (fixes #44)

Before we proceed to other security properties, we will start with the 
\(l\)-bit problem.
We will now analyse how much damage leaking those \(l\) bits of the second 
response does.

>>>>

Before we proceed to other security properties, we will address the \(l\)-bit 
problem:
what advantage does the adversary get from those \(l\) leaked bits of the 
second response?
